The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-02 outputs/paper/paper.Rmd
Introduction writing

You can and should cross-reference sections and sub-sections. For instance, Section \@ref(data). R Markdown automatically makes the sections lower case and adds a dash to spaces to generate labels, for instance, Section \@ref(first-discussion-point).

# Data
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")

urban_rural <- pivot_longer(data[1:2, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -c(Variable, Received_Immunization), names_to="immune_status", values_to="value")
population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)

@@

```{r}
population %>%
  ggplot(aes(x = Variable, y = Population, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
Talk more about it.

Also bills and their average (Figure \@ref(fig:billssssss)). (Notice how you can change the height and width so they don't take the whole page?)

```{r}
total %>%
  ggplot(aes(x = immune_status, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

Talk way more about it.

# Model

>>>>

The introduction is self-contained and tells a reader everything they need to know including: 1) broader context to motivate; 2) some detail about what the paper is about; 3) a clear gap that needs to be filled; 4) what was done; 5) what was found; and 6) why it is important. A reader should be able to read only the introduction and have a good idea about the research that was carried out.

Trust is a big matter in this world. Especially when you need assistance from areas that you are unfamiliar with, trust is the best thing that you can rely on. For instance, if you need a lawyer, the best thing that you can do is trust him/her/the, and be 100% honest to your lawyer. In medical field, trust directly relates to your life. We are certain that you have observed that many people have been refusing to get vaccine for COVID-19. Then, we start to wonder whether the COVID-19 vaccine controversy is similar to other vaccines that are proved and guaranteed safety such as BCG vaccine for preventing tuberculosis. It is true that we no longer have doubts against them. However, we thought that if you move sight to developing country in 1980~1990s, situation would certainly different because of well constructed healthcare system or other reasons. This curiosty triggered us to start this research.

This paper is about children immunization reports in 1987 Thailand. Specifically how the rate differs between communities, regions, people with different education levels and religion. Along with that, its cases are divided into reports from mothers and healthcare. There clearly exists limitations and gaps that we need to fill. First, we are now in 2022. We cannot go back to the period and conduct research regarding our focus. Second, thoughts cannot be measured thoroughly.

# Data
To obtain data with respect to our interest, we took an approach to Thailand DHS survey in 1980s and 1990s. Among many candidates, we chose year 1987. In the survey, there existed many data similar to our aim. For instance, a data presented child and infant mortality with respect to participants' features. It showed the mortality rate with same variables that our data has. However, we thought that mortality alone could not be enough to show the gap existed between healthcare system and mothers. Following that, we made a decision that combining other variables would cause bias in this research. 
The data we chose presents cases of children immunization status between communities(urban and rural), region(north,northeast,central,south and Bangkok), education level(no education, primary, secondary and higher), religion: (Buddhist and Islam), and whether they were reported from healthcare or mother, or their children did not get one or not. For a small drawback, other religions such as Christianity was excluded since majority of Thai believed Buddhism and almost rest believed Islam.  
Now let's begin to talk about our data in details.

1) Communities
- Urban
- Rural

Surprisingly, in 1987 Thailand, if you take a look at figure\@ref(fig:fig1), there were more people in rural  than urban areas. According to Statistic, urbanization rate in Thailand from 2010 to 2020  slowly increased but it still remained mid 40 percentage to 50 percentage. This is very small compared to that of US, which is mid 70 to 80. In addition to the population density between urban and rural, mother's report cases were extremely more than healthcare in rural area. Calculating the percentage, it was 60 and 22.8 percentage. On the other hand, there seems comparatively similar cases from healthcare and mothers in urban areas. Lastly,immunization rate is higher in urban compared to rural areas.

2) Region
- North
- Northeast
- Central
- South
- Bangkok

As we have observed in figure\@ref(fig:fig1), figure\@ref(fig:fig2) shows regional based immunization status. Most participants were not from Bangkok, the capital of Thailand. Instead, they were from Northeast. This is because Islan, the northeast part of Thailand, is the largest region of Thailand, and urbanization in Thailand is relatively low. The graph shows very similar trends observed in \@ref(fig:fig1). There were more mother's reports outside of Bangkok, and less immunization rate outside of Bangkok. One thing to notice is that percentage of mother's reports in Northeast is noticeably higher.

3) Education level
- No Education
- Primary
- Secondary
- Higher

If you look at figure\@ref(fig:fig4), you can observe that as education level goes up, gap between mother's report and healthcare is being equalized. In addition to that, non immunization rate decreases. One thing to notice is that higher education you have in Thailand there existed more immunization rate. For instance, people with higher education shows immunization rate close to 100%.

4) Religion
- Buddhist
- Islam

We have discussed about small drawback in religion, which is other religion except Buddhisms and Islam were not collected. Further, majority of Thai people believes in Buddhism, thus in the graph figure\@ref(fig:fig4), you can observe that there existed more cases in Buddhism than Islam. As we observed up to this point, similar to other variables, there existed more mother's report cases than that of healthcare with no exception to religion. 
```{r, include=FALSE, echo=FALSE}
# Read the extracted and cleaned data, data extraction done in 01-gather-data.R and modification done in 02-clean-and-prepare-data.R
data <- read_csv("outputs/data/cleaned_data.csv")

urban_rural <- pivot_longer(data[1:2, 1:5], -Variable, names_to="immune_status", values_to="value")
region <- pivot_longer(data[3:7, 1:5], -Variable, names_to="immune_status", values_to="value")
education <- pivot_longer(data[8:11, 1:5], -Variable, names_to="immune_status", values_to="value")
religion <- pivot_longer(data[12:13, 1:5], -Variable, names_to="immune_status", values_to="value")
total <- pivot_longer(data[14, 1:5], -Variable, names_to="immune_status", values_to="value")
population <- data.frame(Variable = data$Variable, Population = data$Number_of_Children)

@@

```{r fig1,echo=FALSE, fig.cap = "Immunization cases between communities"}
population %>%
  ggplot(aes(x = Variable, y = Population, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig2,echo=FALSE, fig.cap = "Immunization cases between communities"}
#ggplot(data[1:2,], aes(x = Variable, y = Health_Record)) + geom_bar(stat='identity') + facet_wrap(~Mothers_Report)
urban_rural %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig3,echo=FALSE, fig.cap = "Immunization cases between region"}
#ggplot(data[3:7,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
region %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
```{r fig4,echo=FALSE, fig.cap = "Immunization cases between education"}
#ggplot(data[8:11,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
education %>%
  ggplot(aes(x = Variable, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig5,echo=FALSE, fig.cap = "Immunization cases between religion"}
#ggplot(data[12:13,], aes(x = Variable, y = Health_Record, fill = Variable)) + geom_bar(stat='identity')
religion %>%
  ggplot(aes(x = immune_status, y = value, fill = Variable)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```

```{r fig6,echo=FALSE, fig.cap = "Immunization and non-immunization cases total"}
total %>%
  ggplot(aes(x = immune_status, y = value, fill = immune_status)) +
  geom_bar(stat='identity', position = "dodge") +
  coord_flip()
```
